\textbf{Optimization of Porous Silicon (PSi) with gradient refractive index (GRIN): A comparison with computational schemes with experimental results }

### 2020-06-04 paper.tex
Added some comments.

\documentclass[12pt,letterpaper,onecolumn,twoside]{article}
\usepackage[spanish]{babel}
\usepackage[left=2cm,right=2cm,top=1.5cm,bottom=1.5cm]{geometry}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{}\lhead{}\chead{}\rhead{}
\renewcommand{\headrulewidth}{0pt}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage{subfigure} % subgráfico
\usepackage{lscape}
\usepackage{setspace}
\usepackage{enumitem}
\usepackage[noblocks]{authblk}
\usepackage{float}
\usepackage{cite}% para contraer referencias
\usepackage[usenames]{color}
\providecommand{\abs}[1]{\lvert#1\rvert}
\providecommand{\norm}[1]{\lVert#1\rVert}
 \title{\textbf{Optimization of Porous Silicon (PSi) with gradient refractive index (GRIN): A comparison with computational schemes with experimental results } }

\author[1]{C. A. Ospina de la Cruz}
\author[2]{W. L. Mochan }
\author[3]{V. Agarwal }

\affil[1]{{\scriptsize Posgrado en Ingenier\'ia y Ciencias Aplicadas del Centro de Investigación en Ingenier\'ia y Ciencias Aplicadas (CIICAp-IICBA), Universidad Autónoma del Estado de Morelos (UAEM), Cuernavaca CP 62209, México}}
\affil[2]{{\scriptsize Instituto de Ciencias F\'isica ,Universidad Nacional Autonoma de Mexico, Av. Universidad S/N, Col. Chamilpa, 62210 Cuernavaca, Morelos, Mexico  } }
\affil[3]{{\scriptsize Centro de Investigaci\'on en Ingenier\'ia y Ciencias Aplicadas,Universidad del Estado de Morelos, Av. Universidad 1001 Col. Chamilpa, Cuernavaca, Morelos 62209, Mexico  } }
\affil[*]{{\scriptsize Corresponding author: xxxxxx@xxxx.xxx}}
\date{}

\begin{document}
\renewcommand{\contentsname}{Contents}
\renewcommand{\abstractname}{Abstract}
\renewcommand{\tablename}{Table}
\vspace{50pt}

\maketitle
\begin{abstract}
We propose a simple setup which allows the calculation of the current
density as a function of position within an electrochemical cell used
to produce porous Silicon structures with a controlled gradient in their
index of refraction. We produced samples under several conditions and
characterized them with scanning electron microscopy, and
ultraviolet-visible-near infrared reflectance spectroscopy. Our
results allow us to obtain from experiments on a single or just a few
samples a full characterization of the dependence of porosity,
dielectric function and speed of attack on the current density and on
position, so that novel nonhomogeneous devices may be designed and
built.

Keywords: Porous Silicon; GRIN; Reflectance Spectra.
\end{abstract}

\vspace{-0.8cm}
\singlespacing
\tableofcontents

%\newpage
\spacing{1}

 \section{Introduction}

The structural behavior of nanostructured materials  has  become a
great  topic  of global  interest,  where numerous  research has been
done so far \cite{I1}. We found a great way to go for future
technological  explorations,  countless  challenges and  that  open a
range of possibilities to develop further  study  on these
issues\cite{I2}. Porous silicon (PSi) is a versatile nanostructured
material and an excellent candidate as a technological platform for
different sensing applications \cite{I3, I4}, due to its easy
manufacturing,  large surface area, high surface reactivity,  and
moreover, its optical transduction capacity.  Photonic crystals are
multilayer dielectric structures that have periodicity in the
dielectric function along one direction \cite{I5}. It has numerous
studies for high reflectivity and the ability to adjust  the photonic
prohibited  band (PBG)\cite{I6} , which leads to possible applications
such as filters\cite{I7}, optical switches\cite{I8}, omnidirectional
mirrors\cite{I9}, waveguides for PC \cite{I10} etc. In the
conventional manufacturing of PSi the desired result  is to obtain
homogeneous samples (same structural characteristics) from the
periphery  to the center  of the electrochemically  attacked area.
However, with an asymmetric anodizing configuration,  samples with a
lateral gradient in terms of pore size and thickness of the porous
layer are obtained \cite{I101}. In this configuration,  the face of
the platinum  electrode (cathode)  is relatively maintained
perpendicular  to the surface of the Si substrate (anode) at one end
of the cell, so that the distribution of the current within the
electrolyte  solution varies depending on the distance  of the
electrode due to the resistance of the electrolyte,  resulting  in a
decrease in current density as the distance from the electrode
increases \cite{I102, I103}. The result is a porous surface with
different pore sizes ranging from a few nanometers  to pores on the
order of a few micrometers  \cite{I104}. The dimensions of the pores
obtained on the same chip can be controlled by adjusting the anodizing
current and electrolyte concentration \cite{I11}. Currently, these
types of samples have found their application relevant as optical band
filters \cite{I12}, devices with a multidirectional photonic band
(photonic bar codes) \cite{I13} and mainly as biosensors. In this way,
the effect of different topographies (porosities in the same sample)
on the culture / adhesion of certain cells \cite{I14} is studied,
considerably reducing the number of samples and cost of the study. In
addition, they are also very useful when a biomolecule size-exclusion
technique is required allowing the identification and separation of
these biological compounds \cite{I15}. Recent studies  have shown that
the  combination  of thermal  oxidation  and infiltration of TiO2   by
ALD offers the  opportunity to manufacture  a high index of refraction
of contrast, visibly transparent GRIN optical elements from PSi
absorbent structures \cite{I16}. A Despite previous research on the
formation of porous silicon with GRIN, type p in manufacturing and
characterization, there was no control of current densities, much less
a model that  explained said lateral  gradient. In this work, we
reported a gradient refractive index (GRIN) structure by varying the
current density on the fabrication of porous silicon photonic
structure. This current density values, depth, and porosity of the
photonic structure were calculated from an electrostatic model for
photonic crystals with a gradient refractive index
(EMPCGRIN). Moreover, the theoretical and experimental studies were
exhibited similar results.

@@

The calculate  current density in a GRIN structure produced by an
electrochemical attack on Si to produce Porous Si with a
position-dependent porosity due to the distance to the counter
electrode. A simplifies  calculation  with geometry,
assumimg  in the form of a whole prism on the sides a, b, c with a, b
horizontal and c vertical. Here c considered as the height of the
liquid, and the walls are insulating, but the bottom is completely
covered with the sample, which act as good conductor. The electrode is
a thin insulated cable with tip, which  a point  current source.
\begin{figure}[H]
  \centering
  \includegraphics[scale=.4]{Images/celdan}
  \caption{\emph{Diagram of the Electrolytic cell where we can see the shape of a prism on the sides a, b, c with a, b horizontal and c vertical. I'll take as the height of the liquid. The walls are insulating, but the bottom is completely covered by the sample, I suppose it is a good conductor. The tip of the electrode is a thin insulated wire located at $ \vec{r}_0 $.}}
\end{figure}
The current in the electrolyte is $ \vec {J} = \sigma \vec{E} $ with $
\sigma $ is the conductivity. This for the stationary case $
\bigtriangledown \cdot \vec{j} = 0 $. The electric field is derived
from the electric potential, $\vec {E} = - \bigtriangledown \varphi
$.
And we can say that $ \bigtriangledown^{2} \varphi = 0 $, since the
sample is a relatively good conductor, when connected to earth $
\varphi(x, y, 0) = 0 $. Integrating $ \vec{J} $ over a small sphere
superimposing the electrode gives $ \int ds \cdot \vec{J} = I $.
The current density that carries the current to the tip. So
\begin{equation}
  \int ds \cdot \vec{E} = \dfrac{I}{\sigma}
\end{equation}
The problem to be solved is thus, to obtain the potential produced by a point charge,
\begin{equation}
  q_{_{0}} = \dfrac{I}{4 \pi \sigma}
\end{equation}
In the positions$\vec{r}_{_{0}}=(x_{_{0}}, y_{_{0}}, z_{_{0}})$ is the
tip of the electrode that is in the presence of a ground conductor
plane grounded $ z = 0 $ and enclosed on the insulating walls at $ (0,
y, z) $, $ (a, y, z) $, $ (x, 0, z) $ , $ (x, b, z) $. The surface of
the liquid is also not conductive to $ (x, y, c) $, the normal current
is $\vec{j} \cdot \hat{n}=0$ and the normal of the field is $ \vec{E}
\cdot \hat{n}=0  $. i.e
\begin{equation}
E_{_{x}}(0, y ,z)= E_{_{x}}(a, y ,z)=E_{{_y}}(x, 0 ,z)=E_{{_y}}(x, b ,z)=E_{{_z}}(x, y ,c)=0
\end{equation}
This has a mixture of Dirichlet-Neumann type boundary conditions. By
using the simplified prism geometry  can solve the problem using the
theory of image loads. Each load has an image of the same sign and
magnitude for each lateral insulating surface and the opposite sign
change in the lower part of the conductive plane, as follows.
 \begin{figure}[H]
 \centering
 \includegraphics[scale=.6]{Images/Cellgrin}
 \caption{\emph{a) Diagram of a rectangular electrolytic cell, with a
     real charge in the corner of the cell with its charges ($ q $)
     images of the same sign in $ Z_0 $ and another charge image ($ -q
     $) with change of sign located below the conductor in position $
     -Z_0 $. b) The upper face seen from above, a real load and its
     image loads in $ Z_0 $. c) All this formed a systems of a real
     load and its image loads produced by the cell walls and its other
     images seen from above, forming a periodic space. }}
 \label{fig:T1}
\end{figure}

@@

\begin{figure}[H]

@@

\section{Discussion and Results}
\subsection{Simulation of the EMPCGRIN model}
 To test the developed  idea in the theoretical section, we find a
 relation of the tip of the counter electrode that acts similarly as a
 point charge and the current density for a geometry in an
 electrolytic box and solve the electrostatic equations with suitable
 boundary conditions. Resulting in an electrostatic model for photonic
 crystals with a refractive index with gradient (EMPCGRIN).
\begin{figure}[H]
  \centering
  \includegraphics[scale=0.7]{Images/G123}
  \caption{\emph{ Simulation to calculate the current density in
      a structure with gradient refractive index (GRIN) produced
      by electrochemical attack on crystalline silicon to
      produce porous silicon (PSi), with a current density
      profile $ J (mA / cm ^ 2 ) $ normalized with the electric
      current $ I (mA) $, we have $ J / I \sim 0.5 \ \ a \ \ 1.2
      (cm^{-2}) $, for a cell of $ a = 2.03 \ \ cm $ y $ b =
      0.62 \ \ cm $, with an electrode height $ Z_0 = 0.96 \ \
      cm $} Eq. (\ref{Eq:J})}.
  \label{fig:DR1}
\end{figure}
We consider Fig. \ref{fig:DR1} which come from solving
Eq. (\ref{Eq:J}), calculating the current density as a function of the
rectangular cell area of $1,206 \ \ cm^2 $,  the programming with the
PERL PDL package and corresponding graph in gnuplot. We optimize the
appropriate values so that our current density adequately attacks
crystalline silicon, giving the gradient effect. We use as length $a =
2.03 \ \ cm $ and width $b = 0.62 \ \ cm $ the height of the solution
is $ c = 1 \ \ cm $ and we could locate the tip of the electrode at $
R_0 = (X_0 = 0.2 , \ \ Y_0 = 0.4 \ \, Z_0 = 0.96) \ \ cm $ and
evaluated at the surface on the silicon interface, in the plane $ Z =
0 $. In this same Figure \ref{fig:DR1}, we obtain a current density
profile $ J (mA / cm^2) $ normalized with the electric current $ I
(mA) $, we have $ J / I \sim 1.2 \ \ a \ \ 0.5 (cm ^{-2}) $, as we see
in Fig. \ref{fig:DR1} a) an effect that happens on the surface of the
sample, a change of contrate due to the different densities of
attacked currents. We see the decay behavior that the profile has as
Fig. \ref{fig:DR1} b) which is a cut on the axis of $ a $. When we
vary the currents we can observe the behavior of changes in the
normalized current density, with the data obtained through the
simulation we could have a better optimization in the design of porous
silicon proposing a new and novel experimental arrangement, in the
same way we can give ourselves an idea by means of the graph of how
the attack would be and the formal side of the pores in the silicon.

@@

\subsection{GRIN Porous Silicon Microcavities}
 \begin{figure}[H]
	\centering
	\includegraphics[scale=0.4]{Images/MicrGrin}
	\caption{\emph{Diagram of a microcavity of porous silicon
            GRIN. Alternate layers are obtained of high (H) refractive
            index $n_{_{Hi}}$ and low (L) refractive index
            $n_{_{Li}}$, where $N_{_{H}}$ is the number of layers for
            $n_{_{Hi}}$ and $N_{_{L}}$ is the number of layers for
            $n_{_{Li}}$. Then,  $d_{_{Hi}}$ is the monolayer thickness
            of  $n_{_{Hi}}$ at that measurement point and $d_{_{Li}}$
            is the monolayer thickness of $n_{_{Hi}}$ at that
            measurement point. Therefore,  $d_{_{i}}$ is the total
            thickness calculated for each of the measurements,
            defining a i = $ A, B, C$. Having the following
            relationship $d_{_{i}} =
            (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) +
            (2d_{_{Hi}})$. }}
	\label{fig:MCGRIN0}
\end{figure}
The Fig. \ref{fig:MCGRIN0} the scheme of  a initially proposed lateral
gradient for monolayers should be shown in section 4.2, where we
designed an electolytic cell suitable for our experiments and giving
us the expected results of the simulation in section 4.1. Now our
purpose is to manufacture more complex photonic structures such as the
Porous silicon microcavities GRIN, taking into account that we start
from having a tip electrode almost on the surface and by making a
variation of currents we can achieve the effect of alternating the
layers. Alternate layers are obtained of high (H) refractive index
$n_{_{Hi}}$ and low (L) refractive index $n_{_{Li}}$, where $N_{_{H}}$
is the number of layers for  $n_{_{Hi}}$ and $N_{_{L}}$ is the number
of layers for $n_{_{Li}}$. Then,  $d_{_{Hi}}$ is the monolayer
thickness of  $n_{_{Hi}}$ at that measurement point and $d_{_{Li}}$ is
the monolayer thickness of $n_{_{Hi}}$ at that measurement
point. Therefore,  $d_{_{i}}$ is the total thickness calculated for
each of the measurements, defining a i = $ A, B, C$. Having the
following relationship $d_{_{i}} =
(N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$.
Initial data for conventional design we use  $\lambda_{_{c}}= 0.67 \ \
\mu m$, $n_{_{H}} =2.6$, $P_{_{H}} =0.46$, $d_{_{H}}=0.066 \ \ \mu m
$, $t_{_{H}}=35 s  $ y para  $n_{_{L}}= 1.4$,  $P_{_{L}} =0.75$,
$d_{_{L}}=0.117 \ \ \mu m  $, $t_{_{L}}=11 s  $. All these data are
for the point $ 0 $ which is located at one end of the sample just
below the tip counter-electrode.
\begin{figure}[H]
  \centering
  \includegraphics[scale=.5]{Images/MCGRIN2}
  \caption{\emph{a) Three locations at different points are
      considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B
      (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $, from the PSiMCGRIN
      sample $ GMC $. b) We have the reflectance measurements to
      know the optical properties with the proposed
      simulation. We were able to show that in a Porous Silicon
      GRIN structure, for a microcavity the data is very
      consistent with the simulation and the experiment, we
      found the refractive indices and the porosities as a
      function of the current density at each measurement point,
      see Table \ref{tabla:1}. }}
  \label{fig:MCGRIN3}
\end{figure}

>>>>

\documentclass{article}
\usepackage{amsmath}
\usepackage{graphicx} % gráficos
\usepackage[noblocks]{authblk}
%\usepackage{float}
%\usepackage{cite}% para contraer referencias
%\usepackage[usenames]{color}
\newcommand{\abs}[1]{\lvert#1\rvert}
\usepackage{xcolor}
\newcommand{\notaL}[1]{{\color{blue}L:#1}}
\title{\textbf{Optimization of Porous Silicon (PSi) with gradient refractive index (GRIN): A comparison with computational schemes with experimental results } }

\author[1]{C. A. Ospina de la Cruz}
\author[2]{W. L. Mochán }
\author[3]{V. Agarwal }

\affil[1]{Posgrado en Ingenier\'ia y Ciencias Aplicadas del Centro de
  Investigación en Ingenier\'ia y Ciencias Aplicadas (CIICAp-IICBA),
  Universidad Autónoma del Estado de Morelos (UAEM), Cuernavaca CP
  62209, México}
\affil[2]{Instituto de Ciencias F\'isica ,Universidad Nacional
  Autonoma de Mexico, Av. Universidad S/N, Col. Chamilpa, 62210
  Cuernavaca, Morelos, Mexico}
\affil[3]{Centro de Investigaci\'on en Ingenier\'ia y Ciencias
  Aplicadas,Universidad del Estado de Morelos, Av. Universidad 1001
  Col. Chamilpa, Cuernavaca, Morelos 62209, Mexico  }
\begin{document}

\maketitle
\notaL{Quité los intentos de tipografiar. Que de eso se encargue la
  revista.}
\notaL{Cambié la codificación a utf8; ya no uses latin1, es obsoleto.}
\notaL{Quité las líneas kilométricas. No te ocupes de su longitud y no
  juntes mis líneas.}
\notaL{Quité paquetes no escenciales}
\notaL{Cuida de no poner espacios al final de las líneas.}

\begin{abstract}
We propose a simple setup which allows the calculation of the current
density as a function of position within an electrochemical cell used
to produce porous Silicon structures with a controlled gradient in their
index of refraction. We produced samples under several conditions and
characterized them with scanning electron microscopy, and
ultraviolet-visible-near infrared reflectance spectroscopy. Our
results allow us to obtain from experiments on a single or just a few
samples a full characterization of the dependence of porosity,
dielectric function and speed of attack on the current density and on
position, so that novel nonhomogeneous devices may be designed and
built.

Keywords: Porous Silicon; GRIN; Reflectance Spectra.
\end{abstract}
\notaL{Cambié el abstract, pero habrá que revisarlo después.}
 \section{Introduction}

The structural behavior of nanostructured materials  has  become a
topic  of global  interest,  where numerous  research has been
done so far \cite{I1}. We found a great way to go for future
technological  explorations,  countless  challenges and  that  open a
range of possibilities to develop further  study  on these
issues\cite{I2}. Porous silicon (PSi) is a versatile nanostructured
material and an excellent candidate as a technological platform for
different sensing applications \cite{I3, I4}, due to its easy
manufacturing,  large surface area, high surface reactivity,  and
moreover, its optical transduction capacity.  Photonic crystals are
multilayer dielectric structures that have periodicity in the
dielectric function along one direction \cite{I5}. It has numerous
studies for high reflectivity and the ability to adjust  the photonic
prohibited  band (PBG)\cite{I6} , which leads to possible applications
such as filters\cite{I7}, optical switches\cite{I8}, omnidirectional
mirrors\cite{I9}, waveguides for PC \cite{I10} etc. In the
conventional manufacturing of PSi the desired result  is to obtain
homogeneous samples (same structural characteristics) from the
periphery  to the center  of the electrochemically  attacked area.
However, with an asymmetric anodizing configuration,  samples with a
lateral gradient in terms of pore size and thickness of the porous
layer are obtained \cite{I101}. In this configuration,  the face of
the platinum  electrode (cathode)  is relatively maintained
perpendicular  to the surface of the Si substrate (anode) at one end
of the cell, so that the distribution of the current within the
electrolyte  solution varies depending on the distance  of the
electrode due to the resistance of the electrolyte,  resulting  in a
decrease in current density as the distance from the electrode
increases \cite{I102, I103}. The result is a porous surface with
different pore sizes ranging from a few nanometers  to pores on the
order of a few micrometers  \cite{I104}. The dimensions of the pores
obtained on the same chip can be controlled by adjusting the anodizing
current and electrolyte concentration \cite{I11}. Currently, these
types of samples have found their application relevant as optical band
filters \cite{I12}, devices with a multidirectional photonic band
(photonic bar codes) \cite{I13} and mainly as biosensors. In this way,
the effect of different topographies (porosities in the same sample)
on the culture / adhesion of certain cells \cite{I14} is studied,
considerably reducing the number of samples and cost of the study. In
addition, they are also very useful when a biomolecule size-exclusion
technique is required allowing the identification and separation of
these biological compounds \cite{I15}. Recent studies  have shown that
the  combination  of thermal  oxidation  and infiltration of TiO2   by
ALD offers the  opportunity to manufacture  a high index of refraction
of contrast, visibly transparent GRIN optical elements from PSi
absorbent structures \cite{I16}. A Despite previous research on the
formation of porous silicon with GRIN, type p in manufacturing and
characterization, there was no control of current densities, much less
a model that  explained said lateral  gradient. In this work, we
reported a gradient refractive index (GRIN) structure by varying the
current density on the fabrication of porous silicon photonic
structure. This current density values, depth, and porosity of the
photonic structure were calculated from an electrostatic model for
photonic crystals with a gradient refractive index
(EMPCGRIN). Moreover, the theoretical and experimental studies were
exhibited similar results.

@@

The calculate  current density in a GRIN structure produced by an
electrochemical attack on Si to produce Porous Si with a
position-dependent porosity due to the distance to the counter
electrode. A simplifies  calculation  with geometry,
assumimg  in the form of a whole prism on the sides a, b, c with a, b
horizontal and c vertical. Here c considered as the height of the
liquid, and the walls are insulating, but the bottom is completely
covered with the sample, which act as good conductor. The electrode is
a thin insulated cable with tip, which  a point  current source.
\begin{figure}
  \centering
  \includegraphics[scale=.4]{Images/celdan}
  \caption{\emph{Diagram of the Electrolytic cell where we can see the shape of a prism on the sides a, b, c with a, b horizontal and c vertical. I'll take as the height of the liquid. The walls are insulating, but the bottom is completely covered by the sample, I suppose it is a good conductor. The tip of the electrode is a thin insulated wire located at $ \vec{r}_0 $.}}
\end{figure}
The current in the electrolyte is $ \vec {J} = \sigma \vec{E} $ with $
\sigma $ is the conductivity. This for the stationary case $
\bigtriangledown \cdot \vec{j} = 0 $. The electric field is derived
from the electric potential, $\vec {E} = - \bigtriangledown \varphi
$.
And we can say that $ \bigtriangledown^{2} \varphi = 0 $, since the
sample is a relatively good conductor, when connected to earth $
\varphi(x, y, 0) = 0 $. Integrating $ \vec{J} $ over a small sphere
superimposing the electrode gives $ \int ds \cdot \vec{J} = I $.
The current density that carries the current to the tip. So
\begin{equation}
  \int ds \cdot \vec{E} = \dfrac{I}{\sigma}
\end{equation}
The problem to be solved is thus, to obtain the potential produced by a point charge,
\begin{equation}
  q_{_{0}} = \dfrac{I}{4 \pi \sigma}
\end{equation}
In the positions$\vec{r}_{_{0}}=(x_{_{0}}, y_{_{0}}, z_{_{0}})$ is the
tip of the electrode that is in the presence of a ground conductor
plane grounded $ z = 0 $ and enclosed on the insulating walls at $ (0,
y, z) $, $ (a, y, z) $, $ (x, 0, z) $ , $ (x, b, z) $. The surface of
the liquid is also not conductive to $ (x, y, c) $, the normal current
is $\vec{j} \cdot \hat{n}=0$ and the normal of the field is $ \vec{E}
\cdot \hat{n}=0  $. i.e
\begin{equation}
E_{_{x}}(0, y ,z)= E_{_{x}}(a, y ,z)=E_{{_y}}(x, 0 ,z)=E_{{_y}}(x, b ,z)=E_{{_z}}(x, y ,c)=0
\end{equation}
This has a mixture of Dirichlet-Neumann type boundary conditions. By
using the simplified prism geometry  can solve the problem using the
theory of image loads. Each load has an image of the same sign and
magnitude for each lateral insulating surface and the opposite sign
change in the lower part of the conductive plane, as follows.
 \begin{figure}
 \centering
 \includegraphics[scale=.6]{Images/Cellgrin}
 \caption{\emph{a) Diagram of a rectangular electrolytic cell, with a
     real charge in the corner of the cell with its charges ($ q $)
     images of the same sign in $ Z_0 $ and another charge image ($ -q
     $) with change of sign located below the conductor in position $
     -Z_0 $. b) The upper face seen from above, a real load and its
     image loads in $ Z_0 $. c) All this formed a systems of a real
     load and its image loads produced by the cell walls and its other
     images seen from above, forming a periodic space. }}
 \label{fig:T1}
\end{figure}

@@

\begin{figure}

@@

\section{Discussion and Results}
\subsection{Simulation of the EMPCGRIN model}
 To test the developed  idea in the theoretical section, we find a
 relation of the tip of the counter electrode that acts similarly as a
 point charge and the current density for a geometry in an
 electrolytic box and solve the electrostatic equations with suitable
 boundary conditions. Resulting in an electrostatic model for photonic
 crystals with a refractive index with gradient (EMPCGRIN).
\begin{figure}
  \centering
  \includegraphics[scale=0.7]{Images/G123}
  \caption{\emph{ Simulation to calculate the current density in
      a structure with gradient refractive index (GRIN) produced
      by electrochemical attack on crystalline silicon to
      produce porous silicon (PSi), with a current density
      profile $ J (mA / cm ^ 2 ) $ normalized with the electric
      current $ I (mA) $, we have $ J / I \sim 0.5 \ \ a \ \ 1.2
      (cm^{-2}) $, for a cell of $ a = 2.03 \ \ cm $ y $ b =
      0.62 \ \ cm $, with an electrode height $ Z_0 = 0.96 \ \
      cm $} Eq. (\ref{Eq:J})}.
  \label{fig:DR1}
\end{figure}
We consider Fig. \ref{fig:DR1} which come from solving
Eq. (\ref{Eq:J}), calculating the current density as a function of the
rectangular cell area of $1,206 \ \ cm^2 $,  the programming with the
PERL PDL package and corresponding graph in gnuplot. We optimize the
appropriate values so that our current density adequately attacks
crystalline silicon, giving the gradient effect. We use as length $a =
2.03 \ \ cm $ and width $b = 0.62 \ \ cm $ the height of the solution
is $ c = 1 \ \ cm $ and we could locate the tip of the electrode at $
R_0 = (X_0 = 0.2 , \ \ Y_0 = 0.4 \ \, Z_0 = 0.96) \ \ cm $ and
evaluated at the surface on the silicon interface, in the plane $ Z =
0 $. In this same Figure \ref{fig:DR1}, we obtain a current density
profile $ J (mA / cm^2) $ normalized with the electric current $ I
(mA) $, we have $ J / I \sim 1.2 \ \ a \ \ 0.5 (cm ^{-2}) $, as we see
in Fig. \ref{fig:DR1} a) an effect that happens on the surface of the
sample, a change of contrate due to the different densities of
attacked currents. We see the decay behavior that the profile has as
Fig. \ref{fig:DR1} b) which is a cut on the axis of $ a $. When we
vary the currents we can observe the behavior of changes in the
normalized current density, with the data obtained through the
simulation we could have a better optimization in the design of porous
silicon proposing a new and novel experimental arrangement, in the
same way we can give ourselves an idea by means of the graph of how
the attack would be and the formal side of the pores in the silicon.

@@

\subsection{GRIN Porous Silicon Microcavities}
 \begin{figure}
	\centering
	\includegraphics[scale=0.4]{Images/MicrGrin}
	\caption{\emph{Diagram of a microcavity of porous silicon
            GRIN. Alternate layers are obtained of high (H) refractive
            index $n_{_{Hi}}$ and low (L) refractive index
            $n_{_{Li}}$, where $N_{_{H}}$ is the number of layers for
            $n_{_{Hi}}$ and $N_{_{L}}$ is the number of layers for
            $n_{_{Li}}$. Then,  $d_{_{Hi}}$ is the monolayer thickness
            of  $n_{_{Hi}}$ at that measurement point and $d_{_{Li}}$
            is the monolayer thickness of $n_{_{Hi}}$ at that
            measurement point. Therefore,  $d_{_{i}}$ is the total
            thickness calculated for each of the measurements,
            defining a i = $ A, B, C$. Having the following
            relationship $d_{_{i}} =
            (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) +
            (2d_{_{Hi}})$. }}
	\label{fig:MCGRIN0}
\end{figure}
The Fig. \ref{fig:MCGRIN0} the scheme of  a initially proposed lateral
gradient for monolayers should be shown in section 4.2, where we
designed an electolytic cell suitable for our experiments and giving
us the expected results of the simulation in section 4.1. Now our
purpose is to manufacture more complex photonic structures such as the
Porous silicon microcavities GRIN, taking into account that we start
from having a tip electrode almost on the surface and by making a
variation of currents we can achieve the effect of alternating the
layers. Alternate layers are obtained of high (H) refractive index
$n_{_{Hi}}$ and low (L) refractive index $n_{_{Li}}$, where $N_{_{H}}$
is the number of layers for  $n_{_{Hi}}$ and $N_{_{L}}$ is the number
of layers for $n_{_{Li}}$. Then,  $d_{_{Hi}}$ is the monolayer
thickness of  $n_{_{Hi}}$ at that measurement point and $d_{_{Li}}$ is
the monolayer thickness of $n_{_{Hi}}$ at that measurement
point. Therefore,  $d_{_{i}}$ is the total thickness calculated for
each of the measurements, defining a i = $ A, B, C$. Having the
following relationship $d_{_{i}} =
(N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$.
Initial data for conventional design we use  $\lambda_{_{c}}= 0.67 \ \
\mu m$, $n_{_{H}} =2.6$, $P_{_{H}} =0.46$, $d_{_{H}}=0.066 \ \ \mu m
$, $t_{_{H}}=35 s  $ y para  $n_{_{L}}= 1.4$,  $P_{_{L}} =0.75$,
$d_{_{L}}=0.117 \ \ \mu m  $, $t_{_{L}}=11 s  $. All these data are
for the point $ 0 $ which is located at one end of the sample just
below the tip counter-electrode.
\begin{figure}
  \centering
  \includegraphics[scale=.5]{Images/MCGRIN2}
  \caption{\emph{a) Three locations at different points are
      considered, denoted as follows, $ A (0.3 \ \ cm) $ and $ B
      (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $, from the PSiMCGRIN
      sample $ GMC $. b) We have the reflectance measurements to
      know the optical properties with the proposed
      simulation. We were able to show that in a Porous Silicon
      GRIN structure, for a microcavity the data is very
      consistent with the simulation and the experiment, we
      found the refractive indices and the porosities as a
      function of the current density at each measurement point,
      see Table \ref{tabla:1}. }}
  \label{fig:MCGRIN3}
\end{figure}

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|c|c|c|c|}
    \hline
    \textbf{Points} & $\lambda_c (\mu m)$ & \textbf{n} & \textbf{k} & \textbf{Porosity} & \textbf{J}$(mA/cm^2)$ & \textbf{t(s)}\\
    \hline
    A(H) & 0.65 & 2.661 & 0.0264 & 0.45 & 5.5 & 35 \\
    \hline
    B(H) & 0.58 & 2.762 & 0.0135 & 0.41 & 4.0 & 35 \\
    \hline
    C(H) & 0.54 & 2.808 & 0.0178 & 0.39 & 3.0 & 35 \\
    \hline
    A(L) & 0.65 & 1.442 & 0.0015 & 0.74 & 44 & 11 \\
    \hline
    B(L) & 0.58 & 2.295 & 0.0091 & 0.68 & 32 & 11 \\
    \hline
    C(L) & 0.54 & 2.302 & 0.001 & 0.64 & 24 & 11 \\
    \hline
  \end{tabular}
  \caption{ \emph{We have different points denoted as follows, $ A
      (0.3 \ \ cm) $ and $ B (0.8 \ \ cm) $ and $ C (1.2 \ \ cm) $,
      from the sample of a Porous Silicon Microcavity GRIN
      (PSiMCGRIN) $ GMC $. Alternate layers of high refractive index
      (H) and low refractive index (L) are obtained at each of the
      measurement points (A, B and C). The refractive indexes of the
      PSiMCGRIN were considered from the experimental and theoretical
      values that were obtained for the porosity ($ P =
      0.3J^{0.24}$). And we could obtain the attack time with the
      relation of $ V = 0.53J ^ {0.79} $ where $ t = d / V $.}}
	\label{tabla:1}
\end{table}
In Fig. \ref{fig:MCGRIN3} a) Three locations at different points are
considered, denoted as follows, $ A (0.3 \ \ cm) $ , $ B (0.8 \ \ cm)
$ and $ C (1.2 \ \ cm) $, from the PSiMCGRIN sample $ GMC $. Likewise,
Fig. \ref{fig:DR3} b), we have the reflectance measurements to know
the optical properties with the proposed simulation. We can see how
from an experimental setup we have some important results as a result
of a whole calibration curve suitable for making GRIN porous
silicon. The refractive index of the Porous Silicon Microcavities GRIN
were considered the experimental and theoretical values obtained for
the porosity and the thicknesses shown in Table 1. The porous silicon
microcavities (MCSP) with refractive index with gradient (GRIN), were
manufactured with different current densities ranging from $ 6 \ \ mA
/ cm ^ 2 $ to $ 2.5 \ \ mA / cm ^ 2 $ for a current of $ 5 \ \ mA $,
for a $t_{_{H}}=35 s $, with a high refractive index $n_{_{H}} \sim$ $
2,661$ to $ 2,808$ and porosities of $P_{_{H}} \sim$ $ 0.45 $ to $
0.39 $. Also for $ 44 \ \ mA /cm^2 $ to $ 24 \ \ mA / cm^2 $, current
of $ 38 \ \ mA $, using $t_{_{H}}=11 s$  for low refractive index
$n_{_{L}}\sim$ $ 1,448 $ to $ 2,267 $ and with porosities of
$P_{_{H}} \sim$ $0.75 $ to $ 0.64 $. The porosity was calculated with
the calibration curve exposed in the ($ P = 0.3J^{0.24} $). And the
attack time could be obtained with the relation of $ V = 0.53J^{0.79}
$ where $ t = d / V $ and the refractive index using the Bruggeman
formula. For theoretical values, we use complex refractive indices as
free parameters to fit the experimental refractive spectra (Section
4.2).
 \begin{figure}
   \centering
   \includegraphics[scale=.5]{Images/MCGRINSEM}
   \caption{\emph{SEM image of the cross section profile of the
       microcavities with GRIN. The measured thicknesses of the
       complete multi-film structures showed good agreement with the
       simulations taken from $ V = 0.53J ^ {0.79} $ where $d_j=Vt_j$
       ($j=H,L$), which are the thicknesses of each of the monolayer
       of the porous silicon microcavity GRIN at the measurement
       points and the total thickness we find it as $d_{_{i}} =
       (N_{_{Hi}}d_{_{Hi}})+(N_{_{Li}}d_{_{Li}}) + (2d_{_{Hi}})$
       defining $ i = $ A, B, C. Which resulted in (measured /
       simulation) $ 2.25 / 2.31 \ \ \mu m $ (for structure at Point
       A), $ 2.17 / 2.08 \ \ \mu m $ (for structure at point B) and $
       1.87 / 1.65 \ \ \mu m $ (for structure at point C)}}
	\label{fig:MCGRIN4}
\end{figure}
